flowers-pilot-analysis

### 2021-07-29 code/aa-flowers-pilot_analysis.Rmd
created a human-readable transcript to share with group

d.rounds.final <-  d.rounds %>% left_join(d.games %>% select(gameId, conditionName, condition)) %>% 
  filter(conditionName != "coopCartel")%>% anti_join(rounds_exclude)
d.raw_chat.final <- d.raw_chat %>% left_join(d.games %>% select(gameId, conditionName, condition)) %>% 
  filter(conditionName != "coopCartel") %>% anti_join(rounds_exclude) %>% write_csv(here("data/processed_data/joined_data/filtered_raw_chat.csv"))
```

@@

```{r}
d.rounds.final %>% group_by(gameId, repNum, blockNum, trialNum) %>% 
  summarize(num_unique_flowers = n_distinct(playerResponse),
            mean_response_time = mean(time_sec, na.rm = T))  %>%
  left_join(d.games %>% select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(condition != "coopCartel") %>%
  ggplot(aes(x = repNum, y = log(mean_response_time), color = condition, linetype = languageCondition)) + 
  geom_point(alpha = .1) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name), rows = vars(languageCondition)) + labs(x = "Trial Number", y = "log Mean response time")+ scale_color_bay() + theme_jmank()
```

>>>>

#exclude cooperative condition
d.rounds.final <-  d.rounds %>% left_join(d.games %>% select(gameId, conditionName, condition)) %>% 
  filter(conditionName != "coopCartel")%>% anti_join(rounds_exclude)

d.raw_chat.final <- d.raw_chat %>% left_join(d.games %>% select(gameId, conditionName, condition)) %>% 
  filter(conditionName != "coopCartel") %>% anti_join(rounds_exclude) %>% write_csv(here("data/processed_data/joined_data/filtered_raw_chat.csv"))
```

Clean up a sharable data csv
```{r}
joined_data <- d.raw_chat.final %>% select(-c(index, createdAt, 
                               submitted, conditionName)) %>% 
  left_join(d.rounds.final %>% 
              select(gameId, playerId,repNum, blockNum, trialNum, 
                     playerResponse, playerEarnings = playerUtility)) %>% 
  left_join(d.players %>% select(playerId, playerName = name)) %>%
  left_join(d.contexts %>% select(gameId, repNum, blockNum, trialNum, playerResponse = label, responseRawUtility = utility, blinded))
```

@@

```{r}
d.rounds.final %>% group_by(gameId, repNum, blockNum, trialNum) %>% 
  summarize(num_unique_flowers = n_distinct(playerResponse),
            mean_response_time = mean(time_sec, na.rm = T))  %>%
  left_join(d.games %>% select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(condition != "coopCartel") %>%
  ggplot(aes(x = repNum, y = log(mean_response_time), color = condition, linetype = languageCondition)) + 
  geom_point(alpha = .1) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name), rows = vars(languageCondition)) + labs(x = "Trial Number", y = "log Mean response time") + scale_color_bay() + theme_jmank()
```
